Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-13 report/report.tex
Update todo
Merge research question + evaluation, RQ references, restructure restults

\section{Evaluation}

@@

The road features will be categorized according to type, so that the rate of collisions between footpaths and other features can be compared to that of other road types.
OSM mainly makes the distinction between primary, secondary, residential and footpath roads, so this classification will also be used in this report.
The above features will be calculated for each road type separately by summing over each road feature of a certain type.

Following this, an algorithm will find the exact same metrics with regards to how many road features that can in theory be corrected by simple geometrical translation of their vertices.
This will also be preseneted in terms of the number of road features, the number of edges and the total length in meters of remaining colliding road.

@@

@@

\section{Positional accuracy statistics}

@@

For the primary collision study.

Table \ref{table:road-collision} shows the statistics of the collision study, and the number of roads, number of edges and total edge length that showed intersections with other features before road extrusion, by road category.
For footpaths in particular, it was shown that 12.05\% of all roads collide with some other feature after extrusion to the minimum width.
The same was shown to be true for 0.11\% of the road polyline edges and 0.09\% of the total road length.
Table \ref{table:road-collision-corrected} shows the remaining roads, edges and total edges length whose intersections with other features could not be resolved by geometrical translation of a distance smaller than the positional accuracy.
For footpaths this was shown to hold of 0.51\% of all roads, 
The number of road edges and percentage of the total road length that could not be corrected by geometric translation was significantly small.

@@

\section{Completeness by building area}

@@

\section{Building matching statistics}

@@

\section{Shape accuracy statistics}

@@

% Wednesday:
% TODO: Merge 2.1, 2.2
% TODO: 2.1: Add a sentence about where the question fits into the big picture
% TODO: 2.1: Add section refereces to implementation and results of the sub-questions
% TODO: Reduce long section headlines
% TODO: Rename analysis -> conclusions
% TODO: Shorten abstract
% TODO: Verify that citings look correct (compare to other reports)

% Thursday:
% TODO: Abstract: Mention that the scientific study is a contribution
% TODO: Main challenge: How to reconstruct a 3D city. Make this more clear in the abstract
% TODO: Introduction (See meeting log for suggestions)
% TODO: Introduction, picture of a virtual city

>>>>

@@

The road features will be categorized according to type, so that the rate of collisions between footpaths and other features can be compared to that of other road types.
OSM mainly makes the distinction between primary, secondary, residential and footpath roads, so this classification will also be used in this report.
The above features will be calculated for each road type separately by summing over each road feature of a certain type.
Following this, an algorithm will find the exact same metrics with regards to how many road features that can in theory be corrected by simple geometrical translation of their vertices.
This will also be preseneted in terms of the number of road features, the number of edges and the total length in meters of remaining colliding road.

For the collision study, see sections 1.3.1 for an implementation overview, 4.2 for a detailed walkthrough of the program implementation, and 5.1 for the results.

@@

For the positional accuracy study, see sections 1.3.2 for an implementation overview, 4.1 for a walkthrough of the program implementation, and 5.2 for the results.

@@

@@

For the primary collision study.
Table \ref{table:road-collision} shows the statistics of the collision study, and the number of roads, number of edges and total edge length that showed intersections with other features before road extrusion, by road category.
For footpaths in particular, it was shown that 12.05\% of all roads collide with some other feature after extrusion to the minimum width.
The same was shown to be true for 0.11\% of the road polyline edges and 0.09\% of the total road length.
Table \ref{table:road-collision-corrected} shows the remaining roads, edges and total edges length whose intersections with other features could not be resolved by geometrical translation of a distance smaller than the positional accuracy.
For footpaths this was shown to hold of 0.51\% of all roads, 
The number of road edges and percentage of the total road length that could not be corrected by geometric translation was significantly small.

@@

\section{Positional accuracy study}

\section{Secondary metrics}

\subsection{Completeness by building area}

@@

\subsection{Building matching statistics}

@@

\subsection{Shape accuracy statistics}

@@

% Wednesday:
% TODO: Merge 2.1, 2.2
% TODO: 2.1: Add a sentence about where the question fits into the big picture
% TODO: 2.1: Add section refereces to implementation and results of the sub-questions

% Thursday:
% TODO: Verify that citings look correct (compare to other reports)
% TODO: Abstract: Mention that the scientific study is a contribution
% TODO: Main challenge: How to reconstruct a 3D city. Make this more clear in the abstract
% TODO: Introduction (See meeting log for suggestions)
% TODO: Introduction, picture of a virtual city
